DDSAnalytics  - Employee Trends

### 2018-04-10 msds6371-group-project-kaggle.Rmd
Add latest info and graphs

Untransformed Data

@@

Most of the parameter estimates look good except for d3

@@

>>>>

#### Untransformed Data

@@

Most of the parameter estimates look good except for d3, int2 and int3.  However the VIF for all estimates are high (See Image 005), the smallest being 22.  This is another sign that outliers should be investigated.

When looking at the residual plots (Image 006) we can clearly see that Equal Variance is violated when looking athe the Residual and Studentized Residual.  Also, the QQPlot and Histogram displays data that may not be normal.

We need to perform outlier analysis and peform transformations to address equal deviation and normality.

#### Transformed Data

The following transformations were performed to attempt to address the issues found with the untransformed data: Normality and Equal Variance.  Both Log-Linear and Linear-Log did not address these issues with the data.  The final transformation Log-Log did.

##### Log-Log Transformation

When looking at the Log-Log plots (Images 007 to 010) Linearity still holds.  R^2 increased from .57 to .58, and all the VIF's decreased significantly, but some are still above 10.  The d3 and int3 variables are still not statistically significnt, but int2 is now statistically significant.

When looking at residual plots (Image 012), everything looks much better.  Residuals now have equal variance.  The QQ Plot has MUCh less curve to it.  The histogram looks more normal, but still has a left skew.  Cooks-D shows a few points might have some influence on our model.

#### Outlier Analysis

@@

----

#### Plots of Log-Log Data
![BrkSide](images/Log-Log-BrkSide.png)*Image 007*
![Edwards](images/Log-Log-Edwards.png)*Image 008*
![NAmes](images/Log-Log-NAmes.png)*Image 009*
![Other Neighborhoods](images/Log-Log-Others.png)*Image 010*
![MLR Parameter Estimates](images/Log-Log-MLR-Estimates.png)*Image 011*
![MLR Residual Plots](images/Log-Log-MLR-Residuals.png)*Image 012*

----
